---
title: "Homework 1"
author: Sarah McLarnan
date: 2019-09-13
output: github_document
---

##PROBLEM 1
```{r question_1_pt1, message = FALSE}

library(tidyverse)

df_q1 = tibble(
  num_vec = rnorm(8),
  num_vec_pos = num_vec > 0,
  char_vec = c("one", "two", "three", "four", "five", "six", "seven", "eight"),
  fac_vec = factor(c("1", "2", "3", "1", "2", "3", "1", "2"))
)

mean(df_q1$num_vec)
mean(df_q1$num_vec_pos)
mean(df_q1$char_vec)
mean(df_q1$fac_vac)

```
Created dataframe for question 1 with four vector. Attempted to calculate mean of each vectorr. Successfully calculated the means of both the numeric and logical vectors. Recieved errors for the character and factor vectors because they are not numeric or logical. 

```{r question_1_pt2, message = FALSE, eval = FALSE}

as.numeric(df_q1$num_vec_pos)
as.numeric(df_q1$char_vec)
as.numeric(df_q1$fac_vec)

```
The as.numeric converted each vector to numeric. In the case of the logical vector it assigned 0 to FALSE and 1 to TRUE. THe function was unable to assign a number to the character vector and NA was entered. The factor vector was converted to 1, 2, and 3 in line with the factor levels. 


```

```{r, question_1_pt3, message = FALSE}

as.numeric(df_q1$num_vec_pos)*df_q1$num_vec
as.factor(df_q1$num_vec_pos)*df_q1$num_vec
as.numeric(as.factor(df_q1$num_vec_pos))*df_q1$num_vec

```
##PROBLEM 2

```{r, question_2_pt1, message = FALSE}

df_q2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  xy1 = x + y > 1,
  num_xy1 = as.numeric(xy1),
  fac_xy1 = as.factor(xy1)
)

```
The dataset is `r nrow(df_q2)` rows by `r ncol(df_q2)` columns. The mean of variable x is `r mean(df_q2$x)`, the median is `r median(df_q2$x)`, and the standard deviation is `r sd(df_q2$x)`. 

```{r, question_2_pt2, message = FALSE}

library(ggplot2)

plot_x_y = ggplot(df_q2, aes(x=x, y=y)) + geom_point(col="firebrick")
plot_x_y
plot_num_xy1_x = ggplot(df_q2, aes(x=x, y=num_xy1)) + geom_point(col="steelblue")
plot_num_xy1_x
plot_fac_xy1_x = ggplot(df_q2, aes(x=x, y=fac_xy1)) + geom_point(col="gold")
plot_fac_xy1_x

ggsave("homework_1_plot.png", plot=plot_x_y)
```
plot_x_y is a scatter plot of variable y by x seen in red. plot_num_xy1_x is a scatter plot of the numeric vector by x seen in blue. plot_fac_xy1_x is a scatter plot of the factor vector by x seen in yellow. 
